### 2014-10-28 ThesisJo/derivations.tex
la2pdf commit - 2014:10:28	15:36:59	(Tue28.Oct)

We begin by defining the net \textbf{mass flow} through a volumetric element $dV = dx\,dy\,dz$:
%
\begin{align}
\frac{\dot m_\text{net}}{dV} = \frac{\partial \rho\,\v}{\partial x} \ux + \frac{\partial \rho\,\v}{\partial y} \uy + \frac{\partial \rho\,\v}{\partial z} \uz = \nabla \cdot (\rho\v):
\end{align}
%
The space and time dependence of the mass density $\rho = \rho(\p,t)$ and particle velocity $\v = \v(\p,t)$ was omitted here for brevity. If the volume of the element is fixed a change in mass must equal a corresponding change in density. This is the law of \textbf{mass conservation}:
%
\begin{align}
\frac{\partial\rho}{\partial t} = -\nabla \cdot (\rho\v)
\end{align}
%

>>>>

We begin by defining the net \textbf{mass flow} through a volumetric element $dV = dx\,dy\,dz$:
%
\begin{align}
\frac{\dot{\boldsymbol{m}}_\text{net}}{dV} = \ux\frac{\partial \rho\,\v}{\partial x} + \uy\frac{\partial \rho\,\v}{\partial y} + \uz\frac{\partial \rho\,\v}{\partial z} = \nabla \cdot (\rho\v).
\end{align}
%
The space and time dependence of the mass density $\rho = \rho(\p,t)$ and particle velocity $\v = \v(\p,t)$ is omitted here and in the following text for brevity. If the volume of the element is fixed a change in mass must equal a corresponding change in density. This is the law of \textbf{mass conservation}:
%
\begin{align}
\frac{\partial\rho}{\partial t} = -\nabla \cdot (\rho\v).
\end{align}
%
An additional constraint we may surely apply is the Euler's equation, a modification of Newton's second law:
%
\begin{align}
\frac{F}{dV} = \frac{m}{dV} a = \rho\Big(\frac{\partial\v}{\partial t} + \nabla\v\Big) = -\nabla p.
\end{align}
%
